Two applications of logic programming to Coq

### 2021-03-05 papers/types2020/revisions/preamble.tex
starting a revision dir for types20. Initial work on sec 3
cleanup of the code directoty under types2020
Updated acknowledgments

\Copyright{M. Manighetti, D. Miller and A. Momigliano}
%TODO mandatory, please use full first names. LIPIcs license is
%"CC-BY";  http://creativecommons.org/licenses/by/3.0/

@@

 \acknowledgements{Thanks to Enrico Tassi for his help with Coq-Elpi and his comments on the paper.}
\nolinenumbers %uncomment to disable line numbering

@@

% LocalWords:  Matteo Manighetti Inria

>>>>

\Copyright{Matteo Manighetti, Dale Miller and Alberto Momigliano}
%TODO mandatory, please use full first names. LIPIcs license is
%"CC-BY";  http://creativecommons.org/licenses/by/3.0/

@@

 \acknowledgements{Thanks to Enrico Tassi for his help with Coq-Elpi
   and his comments on the paper.  The comments of the anonymous
   reviewers of an early draft of this paper have also been very helpful.} 
\nolinenumbers %uncomment to disable line numbering

@@

% LocalWords:  Matteo Manighetti Inria Palaiseau Ecole Polytechnique
% LocalWords:  Momigliano Dipartimento di Informatica Universit degli
% LocalWords:  studi Milano Coq Tassi Elpi

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
